On the presentation of orthogonal groups over polynomial rings

### 2019-08-01 dl-paper.tex
Notation fix

For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]) &  } \] 
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
Denote by $V$ the subset of \[\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
\[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.
We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
It is clear that this action is well defined.
Denote by $\overline{V}$ the set of orbits of this action.
Whenever two triples $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$ and say that these triples are congruent.
We also use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
We denote by $\overline{p}$ the function $\overline{V} \to \St(\Phi, A[X, X\inv])/G_M^0$ mapping each orbit $(x, [h], u)$ to the coset $p(x, h, u)G_M^0$.

The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
This function is defined for the triples $(g, h, u)$ satisfying $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
If $p(g, h, u)$ happens to belong to $P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
\begin{equation} \label{T_1} t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\end{equation}

From~\cref{SR:additivity} it follows that
\[p\left(t_\alpha(aX^{-1}) (g, h, u)\right) = S_\alpha(a, p(g, h, u)) \in P_\alpha(*) \cdot h_{\alpha}^{-1}(1+am) \subseteq G_M^{\geq 0},\]
therefore the operation $t_\alpha(aX^{-1})$ is well-defined.

\begin{lemma}\label{lem:orbit-action} Let $(A, M)$ be a local pair. 
Then for any $\alpha \in \Phi$ and $a \in A$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$ congruent to $(g, h, u)$.

@@

For $a + Xf \in A + XM[X]$ we can define the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$ by the following identity:
\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, h, u) = (x_\alpha(a + Xf) \cdot g, h\cdot x_{\alpha}(-a), u).  \end{equation}
It is easy to see that this definition is correct.

@@

\begin{lemma} \label{R3_leq0_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}_{d, 1}$ for $d\leq 0$. \end{lemma}
\begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b + Xf)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b \in A + XM[X]$.
Write $b = b_0 + Xf$ for some $f \in M[X]$.
We may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$  (cf. the first part of the proof of~\cref{lem:orbit-action}).
It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b)$, therefore from~\cref{SR:additivity} we obtain that 
\begin{gather*}
\begin{multlined} \nonumber
  \left[T_\beta(b),\ T_\alpha(aX^{-1}) \right] (g, h, u) \sim \\
  \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b_0), u(1-am)\right) = \\ = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, h \cdot h', u] \right) \sim \left(g, h, u\right), \end{multlined} \\
\begin{multlined} \nonumber \text{ where }
 h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b_0) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b_0) = \\
 = h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right),\ x_\beta(b_0)\right] = h_\alpha^{-1}(1-am). \qedhere \end{multlined} \end{gather*}
\end{proof}

\begin{lemma} \label{R3_leqm1_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R2}_{d, 1}$ for $d \leq -1$ . \end{lemma}
\begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
 \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, h, u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, h, u\right). \]

As before, we may assume that $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Since $x_\beta(Xf)$ belongs to $P_\alpha(0)$ we obtain from~\cref{SR:additivity} that:
\begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ h,\ u\right) \sim \\ 
\sim T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am),\ u(1-am)\right) = \\ = \left( [x_\beta(Xf), x_\alpha(aX^{-1})] \cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right),\ u \right) \sim \\ \sim (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ h,\ u). \qedhere \end{multline} \end{proof}

@@

\begin{lemma} \label{R3_1_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R3}_{1,1}^{\angle}$. \end{lemma}
\begin{proof}
Let $\alpha, \beta$ be a pair of roots such that $\alpha$ and $\beta$ form a sharp angle.
We can assume that $p(g, h, u) \in j_+\left(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m')\right)$ for some $m,m' \in M$.
Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
\begin{multline} \nonumber
 T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \end{multline}
where 
\begin{multline} \nonumber
 h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
The expressions in the right-hand sides of the above formulae are clearly symmetric under the action of the transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies that the desired relation holds. 
\end{proof}

\begin{lemma} \label{R2_0_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
\begin{proof} 
\begin{comment}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
\end{comment}
Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m, m' \in M$.
Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
 = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right), u (1 - am) \right) \sim \\
 \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h', u (1 - am) \right) = \\
 = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g, h'', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot$ 
  and the last congruence is obtained as follows:
 \begin{multline} \nonumber
 h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
 = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
 h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right). \qedhere
\end{multline}
\end{proof}

>>>>

For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]) &  } \] 
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, A[X, X\inv])$.
Denote by $V$ the subset of \[\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
\[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.

We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$. This action is well defined since $G^0_M \subset \overline{G}^{\geq 0}_M$. Whenever two triples $v_1, v_2 \in V$ lie in the same orbit we use the notation $v_1 \sim v_2$ and say that they are congruent. The same notation $h_1 \cong h_2$ is also used for the elements of $\St(\Phi, A[X\inv])$ that are right-adjacent with respect to $G^0_M$.

We denote by $\overline{V}$ the set of orbits of this action.
We use the notation $(g, [h], u)$ for the elements of $\overline{V}$.
We denote by $\overline{p}$ the function $\overline{V} \to \overline{G}^{\geq 0}_M/G_M^0$ mapping each orbit $(x, [h], u)$ to the coset $p(x, h, u)G_M^0$.

We start by defining for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
This function is defined for the triples $(g, h, u)$ satisfying $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
If $p(g, h, u)$ belongs to $P_\alpha(m)$ for some $m \in M$, then we define $t_\alpha(aX^{-1})$ by the following identity:
\begin{equation} \label{T_1} t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\end{equation}

From~\cref{SR:additivity} it follows that
\[p\left(t_\alpha(aX^{-1}) (g, h, u)\right) = S_\alpha(a, p(g, h, u)) \in P_\alpha(*) \cdot h_{\alpha}^{-1}(1+am) \subseteq G_M^{\geq 0},\]
therefore $t_\alpha(aX^{-1})$ is well-defined.

\begin{lemma}\label{lem:orbit-action} Let $(A, M)$ be a local pair. 
Then for any $\alpha \in \Phi$ and $a \in A$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on the representative $(g, h \cdot i_+(h_0), u)$, which is congruent to $(g, h, u)$.

@@

For $a + Xf \in A + XM[X]$ we can define the operator $T_\alpha(a + Xf) \colon \overline{V} \to \overline{V}$ by the following identity:
\begin{equation} \label{T_leq0} T_\alpha(a + Xf) \cdot (g, [h], u) = (x_\alpha(a + Xf) \cdot g, [h], u).  \end{equation}
It is easy to see that this definition is correct.

@@

\begin{lemma} \label{R3_leq0_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R3}_{d, 1}$ for $d\leq 0$. \end{lemma}
\begin{proof} We need to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, [h], u) = (g, [h], u)$ for $\beta\in Z(\alpha)$, $a\in A$, $b\in A + XM[X]$.
Write $b = b_0 + Xf$ for some $b_0 \in A$, $f \in M[X]$.
We may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$  (cf. the first part of the proof of~\cref{lem:orbit-action}).
It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b_0)$, therefore by~\cref{SR:additivity} we have
\begin{multline} \nonumber
  \left[T_\beta(b),\ T_\alpha(aX^{-1}) \right] (g, [h], u) = \\
  = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha(-aX^{-1}) \cdot g, [h'], u(1-am)\right) = \\ = \left( [x_\beta(b), x_{\alpha}(aX^{-1})] \cdot g, [h''], u] \right) = \left(g, [h], u\right), \end{multline}
where $h' = h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\beta(b_0)$ and
\begin{multline} \nonumber
 h'' = h' \cdot x_{\alpha}\left(-a(1-am)X^{-1}\right) \cdot x_{\beta}(-b_0) = \\
 = h \cdot h_\alpha^{-1}(1-am) \cdot \left[x_\alpha\left(a(1-am)X^{-1}\right),\ x_\beta(b_0)\right] = h \cdot h_\alpha^{-1}(1-am). \qedhere \end{multline}
\end{proof}

\begin{lemma} \label{R3_leqm1_1} The operators $T_\alpha$ satisfy Steinberg relations of type $\mathrm{R2}_{d, 1}$ for $d \leq -1$ . \end{lemma}
\begin{proof} We need to show that for $a\in A$, $f \in M[X]$ and $\alpha, \beta \in \Phi$ forming an obtuse angle holds
 \[ [T_\beta(Xf),\ T_\alpha(aX^{-1})] (g, [h], u) = \left(x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g, [h], u\right). \]

As before, we may assume that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Since $x_\beta(Xf)$ belongs to $P_\alpha(0)$ we obtain from~\cref{SR:additivity} that:
\begin{multline} \nonumber [T_\beta(Xf),\ T_\alpha(aX^{-1})] \left(g,\ [h],\ u\right) = \\ 
= T_\beta(Xf) \cdot T_\alpha(aX^{-1}) \left(x_{\beta}(-Xf) \cdot x_\alpha(-aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 - am}\right) \cdot h^{-1}_\alpha(1-am)\right],\ u(1-am)\right) = \\ = \left([x_\beta(Xf),\ x_\alpha(aX^{-1})] \cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1 + \tfrac{am}{1-am}}\right)\right],\ u \right) = \\ = (x_{\alpha+\beta}(N_{\beta,\alpha} \cdot af) \cdot g,\ [h],\ u). \qedhere \end{multline} \end{proof}

@@

\begin{lemma} \label{R3_1_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R3}_{1,1}^{\angle}$. \end{lemma}
\begin{proof}
Let $\alpha, \beta$ be a pair of roots such that $\alpha$ and $\beta$ form a sharp angle.
From~\cref{K-a-b} and the proof of the first part of~\cref{lem:orbit-action} it follows that \[p(g, h, u) \in j_+\left(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m')\right)\text{ for some }m,m' \in M.\]
Set $\epsilon = N_{\alpha,-\beta}$. Applying~\cref{SR:sharp} we obtain that
\begin{multline} \nonumber
 T_\beta(bX^{-1}) \cdot T_\alpha(aX^{-1}) \left(g, [h], u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right)\right],\ u(1 + am)\right) = \\ 
 = T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ \left[h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am')\right],\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, [h'], u(1 + am + bm')), \end{multline}
where 
\begin{multline} \nonumber
 h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
If we swapped $(a,\alpha,m)$ with $(b,\beta,m')$, 
the expressions in the right-hand sides of the above formulae would remain unchanged. This implies the required assertion.
\end{proof}

\begin{lemma} \label{R2_0_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
\begin{proof} 
\begin{comment}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
\end{comment}
Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m, m' \in M$.
Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b), T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
 %= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right)\right], u (1 - am) \right) = \\
 = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g,\ [h'],\ u (1 - am) \right) = \\
 = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$  
  and the last equality is obtained as follows:
 \begin{multline} \nonumber
 h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
 = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
 h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right). \qedhere
\end{multline}
\end{proof}
